### 2018-11-09 papers/journal/result-table.tex
removed some spaces

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\def\arraystretch{1.6}
\caption{
{\bf SNARE regulation and graph connectedness.}}
\begin{tabular}{|c|l|l|c|}
\hline
\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness}\\ \thickhline
1. & Boolean function & Boolean function & N = 2C S = 3C \\ \hline
2. & None & Boolean function & N \& S = 3C\\ \hline
3. & Boolean function & SNARE-SNARE inhibition & N \& S = 4C\\ \hline
4. & None & SNARE-SNARE inhibition & No graphs found\\ \hline
5. & Boolean function & None & No graphs found\\ \hline
6. &  None & None & No graphs found\\ \hline

>>>>

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\def\arraystretch{1.6}
\caption{
{\bf SNARE regulation and graph connectedness.}}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\bf{Sr.No} & 	{\multirow{2}{*}{\textbf{Regulation}}} & 
  {\multirow{2}{*}{\textbf{Existential}}} &
{\multirow{2}{*}{\textbf{Universal}}}  \\ 
%	\cline{2-3} &  \cline{Connect & Timing & \\ \hline
%\thickhline

1. & Boolean function & Boolean function & 2C \\ \hline
2. & None & Boolean function & 3C \\ \hline
3. & Boolean function & SNARE-SNARE inhibition & 4C \\ \hline
4. & None & SNARE-SNARE inhibition & No graphs found \\ \hline
5. & Boolean function & None & No graphs found \\ \hline
6. &  None & None & No graphs found \\ \hline
